---
title: "ESM232_DynamicModelsAssignment"
author: "Bridget Gibbons, Kaili Brande"
date: "5/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Implement this model in R (as a differential equation)

```{r}
# Loading necessary packages

library(deSolve)
library(ggplot2)
library(tidyverse)
library(sensitivity)

# Bringing in the model from the .R file

source("forestgrowthmodel.R")



# forest_growth(time = c(1:10), C = 10, r = 0.01, g = 2, closure = 100, K = 500, temp = 20)




```

# 2. Run the model for 300 years (using the ODE solver) starting with an initial forest size of 10 kg/C, and using the following parameters: canopy closure threshold of 100 kgC, a carrying capacity of 500 kg C, a early growth rate of 0.01, a later growth rate of 2 kg/year, and an air temperature of 20C

```{r}

# Defining the initial conditions
initial_C <- 10
closure_thres <- 100
k <- 500
r <- 0.01
g <- 2
air_temp <- 20

# Defining the necessary components for the ode solver
years = seq(from=1, to=300, by=1)
parms = list(closure_thres = 100, k = 500, r = 0.01, g = 2, air_temp = 20)

# Running the solver
results = ode(y = initial_C, times = years, func = forestgrowthmodel, parms = parms)
head(results)

# Assigning column names
colnames(results2)=c("Year","Forest Size")

```

# Graph the results

```{r}

# Converting to a data frame, and graphing the results
results <- as.data.frame(results)

ggplot(results, aes(Year, Forest Size))+geom_point()+labs(y="Forest Size", "Years")

```

# 3. Run a sobol sensitivity analysis that explores how the estimated maximum forest size varies with early and later growth rates. 

```{r}

# Therefore we are measuring the sensitivity of the r (early growth rate) and g (later growth rate) variables



```


# Graph the results of the sensitivity analysis as a box plot and a plot of the two sobol indices (S and T)

```{r}



```

