---
title: "ESM232_DynamicModelsAssignment"
author: "Bridget Gibbons, Kaili Brande"
date: "5/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Implement this model in R (as a differential equation)

```{r}
# Loading necessary packages

library(deSolve)
library(ggplot2)
library(tidyverse)

# Bringing in the model from the .R file

source("")


```

# 2. Run the model for 300 years (using the ODE solver) starting with an initial forest size of 10 kg/C, and using the following parameters: canopy closure threshold of 100 kgC, a carrying capacity of 500 kg C, a early growth rate of 0.01, a later growth rate of 2 kg/year, and an air temperature of 20C

```{r}

initial_C <- 10

closure_thres <- 100
k <- 500

r <- 0.01
g <- 2

air_temp <- 20




```

# Graph the results

```{r}



```

# 3. Run a sobol sensitivity analysis that explores how the estimated maximum forest size varies with early and later growth rates. 

```{r}



```


# Graph the results of the sensitivity analysis as a box plot and a plot of the two sobol indices (S and T)

```{r}



```

