---
title: "ESM232_DynamicModelsAssignment"
author: "Bridget Gibbons, Kaili Brande"
date: "5/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Implement this model in R (as a differential equation)

```{r}
# Loading necessary packages

library(deSolve)
library(ggplot2)
library(tidyverse)
library(sensitivity)

# Bringing in the model from the .R file

source("../esm232_dynamicmodels/forestgrowthmodel.R")



# forest_growth(time = c(1:10), C = 10, r = 0.01, g = 2, closure = 100, K = 500, temp = 20)




```

# 2. Run the model for 300 years (using the ODE solver) starting with an initial forest size of 10 kg/C, and using the following parameters: canopy closure threshold of 100 kgC, a carrying capacity of 500 kg C, a early growth rate of 0.01, a later growth rate of 2 kg/year, and an air temperature of 20C

```{r}

# Defining the initial conditions
C <- 10
closure <- 100
K <- 500
r <- 0.01
g <- 2
temp <- 20

# Defining the necessary components for the ode solver
years = seq(from=1, to=300, by=1)
parms = list(closure = 100, K = 500, r = 0.01, g = 2, temp = 20)

# Running the solver
results = ode(y = C, times = years, func = forestgrowthmodel, parms = parms)
head(results)

# Assigning column names
colnames(results)=c("Year","Forest_Size")

```

# Graph the results

```{r}

# Converting to a data frame, and graphing the results
results <- as.data.frame(results)

ggplot(results, aes(Year, Forest_Size))+geom_point()+labs(y="Forest_Size", "Years")

```

# 3. Run a sobol sensitivity analysis that explores how the estimated maximum forest size varies with early and later growth rates. 

```{r}

# Therefore we are measuring the sensitivity of the r (early growth rate) and g (later growth rate) variables

# obtain parameter sets

# number of parameters

np = 1000

# distributions for parameters

sobol_r = rnorm(mean = 0.01, sd = 0.002, n = np)
sobol_g = rnorm(mean = 2, sd = 0.4, n = np)
X1 = cbind.data.frame(sobol_r, sobol_g)

# repeate distribution sampling

sobol_r = rnorm(mean = 0.01, sd = 0.002, n = np)
sobol_g = rnorm(mean = 2, sd = 0.4, n = np)
X2 = cbind.data.frame(sobol_r, sobol_g)

sobol_forest = sobol2007(model = NULL, X1, X2, nboot = 200)


sim_times = seq(from=1, to=300)
parms = list(r=sobol_forest$X$sobol_r[1], g=sobol_forest$X$sobol_g[1], closure = 100, K = 500, temp = 20)

sens_result = ode(y=C, times=sim_times, func=forestgrowthmodel, parms=parms)

head(sens_result)
colnames(sens_result)=c("time","forest_size")

# turn it into a data frame
sens_result = as.data.frame(sens_result)
ggplot(sens_result, aes(time, forest_size))+geom_point()


# build a function that will extract the information (metrics) you want from your dynamics model (output of the ode)

# create a data structure to store the metrics for each parameter set - lets call it metrics (but could be anything)

compute_metrics = function(result) {
  max_size = max(result$forest_size)
return(list(max_size=max_size))}

######
# I feel ok about the code up until this point, and then I start to get a bit confused... I'm not entirely sure where it's going wrong
######

compute_metrics(sens_result)

# run ODE for each parameter sets to fill in this metrics data structure

wrapper = function(r, g, C, closure, K, temp, sim_times, func) {
    parms = list(r=r, g=g, C = 10, closure = 100, K = 500, temp = 20)
    result = ode(y=C, times=sim_times, func=forestgrowthmodel, parms=parms) 
    colnames(result)=c("time","forest_size")
  # get metrics
  metrics=compute_metrics(as.data.frame(result))
  return(metrics)
}

# send the metrics data structure back to the sensitivity analysis object (from sobel or LHS)

allresults = mapply(FUN=wrapper, r=sobol_forest$X$sobol_r, g=sobol_forest$X$sobol_g,
 MoreArgs=list(C=C, sim_times=sim_times, func=forestgrowthmodel))


allres = as.data.frame(matrix(unlist(allresults), ncol=1, byrow=T))
colnames(allres) = c("max_size")


# create boxplots
tmp = allres %>% gather(key="metric", value="value")
ggplot(tmp, aes(metric, value, col=metric))+geom_boxplot()


sens_tell = sensitivity::tell(sobol_forest, allres$max_size)

# first-order indices (main effect without co-variance)
sens_tell$S

# total sensitivity index -note that this partitions the output variance - so values sum to 1
sens_tell$T

plot(sens_tell)

```


# Graph the results of the sensitivity analysis as a box plot and a plot of the two sobol indices (S and T)

```{r}

sobol_forest_result_graph <- matrix((unlist(allresults)), ncol = 1, byrow = TRUE)
colnames(sobol_forest_result_graph) = c("max_forest_size")

sobol_forest_result_graph_df <- as.data.frame(sobol_forest_result_graph)

sobol_forest_result_2 <- cbind.data.frame(sens_tell$X, mean_value = sens_tell$y)

sobol_forest_result_box <- gather(sobol_forest_result_2, key = "parameter", value = "values", sobol_r, sobol_g)

boxplot <- ggplot(data = sobol_forest_result_box, aes(x = parameter, y = values)) +
    geom_boxplot(aes(color = parameter)) +
    labs(
      title = "Sobol Method",
      x = "Parameters",
      y = "Yield (As Anomaly)"
      ) +
    theme_classic()

boxplot

# Plot of the two sobol indices
plot(sobol_tell)

```

